---
title: "Homework 5"
subtitle: "Mahitha Jangeti"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggplot2)
library(knitr)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

Function that, for a fixed group size, randomly draws “birthdays” for each person; checks whether there are duplicate birthdays in the group; and returns `TRUE` or `FALSE` based on the result.

```{r}
bday_sim = function(n) {
  bdays = sample(1:365, size = n, replace = TRUE)
  any(duplicated(bdays))
}
```

Run this function 10000 times for each group size between 2 and 50

```{r}
sim_results =
  tibble(group_size = 2:50) %>%
  mutate(
    sim_out = map(group_size, ~ rerun(10000, bday_sim(.x))),
    sim_out = map(sim_out, unlist),
    prob = map_dbl(sim_out, mean)
  )
```

Plot if Group size vs Probability of Shared Birthday

```{r}
sim_results %>%
  ggplot(aes(x = group_size, y = prob)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Probability of Shared Birthday vs Group Size",
    x = "Group Size",
    y = "Probability of Shared Birthday"
  ) +
  theme_minimal()
```

Based off the line plot, the larger the group size, the higher the probability of a shared birthday. For example, with a group size of 20 there is approximately 0.38 probability of a shared birthday but for 50 people group size, almost 1.00 probability indicating large likeliness of a shared birthday within a setting. 


## Problem 2

```{r}
```


